### 2016-02-11 AcademicPaperSummaries/PaperSummaries.tex
week 7

\underline{Keywords:} voting behavior, networks
\underline{Research question and research area} This article is looking at testing one of the mechanisms behind why spouses exhibit similar behavior: whether they converge together or pre-select for similarity.\\
\underline{Summary of argument and mechanism} Network mechanism being tested is information exchange through strong ties.\\
\underline{Data \& methods} Experiments in Denver, Co and Minneapolis, MN for 2002 congressional primaries.\\
\underline{Findings} Canvassing resulted in an 8\% increase in propensity to vote among contacted people, and a 5.5 (CO) and 6.5\% (MN) increase among cohabitants of the person contacted. Wording is vague, bit it looks l ike significance didn't meet .05 threshold but did meet .1\\
\underline{Notes on related papers} They're using ``spouse'' and ``roommate'' interchangeably in their mechanism description. This implies that the mechanism is supposed to be just information exchange, particularly in an environment of strong ties, vs pressures driving spouses to similarity.   \\

@@

\underline{Research question and research area} The paper tries to test the contagion and conflict mechanisms of network effects on voting behavior\\
\underline{Summary of argument and mechanism} No proposed mechanism, trying to experimentally test debate in literature about whether conflict or contagion effects are at work in networks of undergrads\\
\underline{Data \& methods} Data is from 14 dorms in election years from 2008-2012\\
\underline{Findings} Findings support contagion, although I suspect that their survey question doesn't quite parse out the question of whether people frequently talk about politics with those whom they disagree. \\
\underline{Notes on related papers}\\

@@

\textbf{Bueno de Mesquita, Ethan and Eric Dickson. 2007. “The Propaganda of the Deed: Terrorism,
Counterterrorism, and Moblization.” American Journal of Political Science 51(2).}

\end{document}

>>>>

\underline{Keywords:} voting behavior, networks
\underline{Research question and research area} This article is looking at testing one of the mechanisms behind why spouses exhibit similar behavior: whether they converge together or pre-select for similarity.\\
\underline{Summary of argument and mechanism} Network mechanism being tested is information exchange through strong ties. Update: he does not talk about mechanism. He's focused on trying to show causality, not mechanism.\\
\underline{Data \& methods} Experiments in Denver, Co and Minneapolis, MN for 2002 congressional primaries.\\
\underline{Findings} Canvassing resulted in an 8\% increase in propensity to vote among contacted people, and a 5.5 (CO) and 6.5\% (MN) increase among cohabitants of the person contacted. Wording is vague, bit it looks like significance didn't meet .05 threshold but did meet .1. Tried to be careful, but could not completely rule out some selection mechanism.\\
\underline{Notes on related papers} They're using ``spouse'' and ``roommate'' interchangeably in their mechanism description. This implies that the mechanism is supposed to be just information exchange, particularly in an environment of strong ties, vs pressures driving spouses to similarity.   \\

@@

\underline{Research question and research area} The paper tries to test the contagion and conflict mechanisms of network effects on voting behavior\\
\underline{Summary of argument and mechanism} No proposed mechanism, trying to experimentally test debate in literature about whether conflict or contagion effects are at work in networks of undergrads\\
\underline{Data \& methods} Data is from 14 dorms in election years from 2008-2012\\
\underline{Findings} Findings support contagion, although I suspect that their survey question doesn't quite parse out the question of whether people frequently talk about politics with those whom they disagree. \\

\underline{Notes on related papers}\\

\textbf{Franzese, R. and J. Hays. 2008. “Interdependence in Comparative Politics: Substance, Theory, Empirics, Substance.” Comparative Political Studies 41: 742–80.}

\underline{Keywords:} spatial processes; diffusion; review

\underline{Research question and research area}\\
\underline{Summary of argument and mechanism} Cite Simmons et al (2005) on four mechanisms of international diffusion: direct/indirect coercion; competition via economic pressures; learning from others' actions; emulation; (they add) migration where some components directly enter others. Strategic interdependence is when some units' actions affect marginal utilities of actions for another.  Free-riding occurs when policies are strategic substitutes.\\
\underline{Data \& methods} Nice overview on pages 753-654 of the models implied by different views of how interconnectedness influences outcome.  \\
\underline{Findings} Case study is from international diffusion of tax policies.\\
\underline{Notes on related papers}\\

@@

Key for the summaries:
\underline{Keywords:}

\underline{Research question and research area}\\
\underline{Model of terrorism}\\
\underline{Summary of argument and mechanism}\\
\underline{Data \& methods}\\
\underline{Findings}\\
\underline{Notes on related papers}\\

\textbf{Bueno de Mesquita, Ethan and Eric Dickson. 2007. “The Propaganda of the Deed: Terrorism,
Counterterrorism, and Mobilization.” American Journal of Political Science 51(2).}

\underline{Keywords:} game theory, terror-state dynamics; public opinion

\underline{Research question and research area} When is terrorism an effective tactic to mobilize public opinion for an extremist group and why can groups provoke states into overreaction? Bueno de Mesquita is in the school that assumes the group-level motivation for attacks is to benefit from government counter-response that radicalizes the group's base and that terror groups and states compete over public opinon.\\
\underline{Model of terrorism} Note that the examples he cites in the motivating examples are generally large guerrilla movements (Hamas, IRA), though he did name check ETA. \\
\underline{Summary of argument and mechanism} Two causal mechanisms: 1) state response tells public whether governments are ``strong'' or ``weak'' type and 2) the economic externalities generated by armed conflict make public inclined to participate by lowering their opportunity costs. Public opinion is altered by level of economic damage inflicted by state counter-terrorism.\\.
\underline{Data \& methods} game theory, PBE solution concept. Actors are state (one of two types), extremist faction, aggrieved population \\
\underline{Findings} Most of analysis dones via comparative statics. ``Findings'' are explorations of implications of the solution spaces.\\
\underline{Notes on related papers} This paper is in a long chain of terrorism papers from EBdM that assume that economic opportunity costs influence recruitment into terrorism. Observe that there are a package of assumptions here that I'm not necessarily sure about, and in particular that terror activity supplants economically-generative activities. Nights-and-weekends operatives don't seem to exist in his world. \\

\textbf{Crenshaw, Martha. 2002. “The Logic of Terrorism: Terrorist Behavior as a Product of Strategic Choice.” in Origins of Terrorism: Psychologies, Ideologies, Theologies, States of Mind, ed. Walter
Reich. p. 54-66.}

\underline{Research question and research area} Description of how terrorism can be the ``expression of a political strategy,'' argues for a way to reconcile group-level rationality with the actions of terror groups. Not theoretically cutting-edge anymore, but Crenshaw always has a great eye for vignette. \\
\underline{Model of terrorism} Terrorism is a choice of organizations that are constrained due to a lack of popular support and, in general, violence is a strategy that group use to compensate for a lack of numbers. Can also follow from technological changes that favor violent groups vs the state (dynamite, transportation, phones) or tactical diffusion. Terrorism has an  ``extremely useful agenda-setting function'' and, in an ideal case (for the group) ``inspires resistance by example'' \\
\underline{Data \& methods} n~/a\\
\underline{Findings} n~/a\\
\underline{Notes on related papers} This paper has been widely re-printed.\\

\textbf{Kydd, Andrew H. and Barbara F. Walter. 2006. “The Strategies of Terrorism,” International
Security Vol. 31, No. 1, p. 49-80.}

\underline{Research question and research area} What strategies to terror groups use and when do they work?\\
\underline{Model of terrorism} Terrorism is the ``use of violence against civilians by non-state actors to attain political goals.'' Give a five-dimension summary of most common goals: regime change, territorial change, policy change, social control, status quo. Also say that information access~/control and regime type are important intervening variables. \\
\underline{Summary of argument and mechanism} Terrorism is a form of costly signaling done by groups that can't impose their will ``by force of arms'' and their violence is designed to persuade audiences to do what they want by imposing costs. ``Terrorists are forced to display publicly just how far they are willing to go to obtain their desired results.''  This happens through five strategies: attrition; intimidation; provocation; spoiling; outbidding\\
\underline{Data \& methods} Mostly a theoretical piece, but does have some summary statistics classifying US-designated organizations by their primary goal. \\
\underline{Findings} n~/a\\
\underline{Notes on related papers} Kydd and Walter propose a typology based on strategy and goals, but they don't connect the attrition and outbidding strategies don't have accompanying goals.\\

\textbf{Min, Eric. 2013. “Taking Responsibility: When and Why Terrorists Claim Attacks.” Paper presented at the 2013 meeting of the APSA and available at http://papers.ssrn.com/sol3/ papers.cfm?abstract\_id=2299920.}

\underline{Keywords:} hypothesis testing; violent political communication

\underline{Research question and research area} When do terror groups claim attacks? (Claims to test Kydd and Walter's theories of strategies.)\\
\underline{Model of terrorism} Frames terror attacks as being essentially a costly signal intended to foment uncertainty. Assumes that claiming credit is risky but that it is an activity that has strategic and communicative value\\
\underline{Summary of argument and mechanism} Groups with a concrete agenda feel that opportunity to spread their message is worth the risk of being associated with violence.\\
\underline{Data \& methods} Data on claimed vs unclaimed attacks from GTD. 27,576 observations. DV is whether the GTD lists the attack as being claimed, IDVs are array of covariates about the attack and group-- not much about the strategic environment. Model is a logit. Also tested on country-level data for Iraq, Pakistan, India, Afghanistan.\\
\underline{Findings} Probability of claim increasing (statistically significantly) in: polity, suicide bombings, GDPPC, existence of other groups, week-long proximity to another attack. Decreasing in: election years, assassination attacks, religious motivation\\
\underline{Notes on related papers} This paper is a theoretical mess, I think that it is ripe for a re-do.\\

\textbf{Plumper, Thomas and Eric Neumayer. 2014. “Terrorism and Counterterrorism: An Integrated Approach and Future Research Agenda.” International Interactions 40(4): 579–589.}

\textit{Note this is in a different style, because I already have a summary}
This is an overview piece.  P\&T provide an overview of their argument, expressed here and elsewhere, that terror organizations are strategic actors. From the strategic actions of terror groups, they conclude that domestic and international targets have differing counter-terror incentives, and particular that international  organizations. The authors conceptually divide the overarching strategy of a group from the proximate strategy of their attack: the latter is influenced by overarching goals but also a function of organizational dynamics of the group as well as the material that they have access to.

T\&P highlight several areas that need more theoretical and analytical work:  most interesting is their description of how organizational structure influences tactical operations, and their division of terror groups into those in which leaders engage in operations (here they use the Red Army Faction as an  exemplar) and those in which leaders direct foot soldiers (such as Usama bin Laden)

There is a nice congruence here with Crenshaw’s argument that terror groups who can afford to field full-time fighters are operationally quite different from those that engage only part-time militants. The former can be more ambitious, but I wonder if they also have a harder time hiding the activities of their operatives (who would have a more difficult time melting back into the population).  Part-time fighters also imply a more geographically restricted 
scope, because they must remain available for their other employment. Also, full-time groups require more funding, which may impose additional constraints.

\underline{Week 9}
\end{document}
